Sequential rank agreement methods for comparison of lists

### 2015-08-09 latex/paper.Rnw
Comments

Most curves start low and then increase indicating higher agreement
among high risk patients.
\textbf{ANDREAS og CLAUS: er det ogsaa forvented eller skyldes det at vi kumulerer fra toppen? agreement boer jo igen vaere hoejt bland low risk patienter ... Claus indsætter måske noget her!}
An exception is the risk prediction agreement for the Lasso tuned with
the AUC criterion which shows very low agreement among the high values
of the predicted risks. The reason is that optimizing the penalty
parameter with respect to the AUC criterion tends to favor a very high
penalty value causing only a single predictor to be selected in each
of the 1000 iterations. This results in a lack of generalizability to
the DACOVA data which gives rise to the higher disagreement in the
predicted risk probabilities. In the extreme case where the penalty
becomes so high that none of the predictors are selected by the Lasso,
the sequential rank agreement for the predicted probabilities becomes
undefined since all the ranks will be ties.

>>>>

Most curves start low and then increase indicating higher agreement
among high risk patients. This is expected if we rank the individuals
according to highest risk of disease. However, it is also expected
that individuals with very low risk also show high agreement. In this
case we order the patients according to (high) risk prediction but we
could essentially also have reversed the order to identify the
patients that have low risk prediction.  An exception is the risk
prediction agreement for the Lasso tuned with the AUC criterion which
shows very low agreement among the high values of the predicted
risks. The reason is that optimizing the penalty parameter with
respect to the AUC criterion tends to favor a very high penalty value
causing only a single predictor to be selected in each of the 1000
iterations. This results in a lack of generalizability to the DACOVA
data which gives rise to the higher disagreement in the predicted risk
probabilities. In the extreme case where the penalty becomes so high
that none of the predictors are selected by the Lasso, the sequential
rank agreement for the predicted probabilities becomes undefined since
all the ranks will be ties.
